Marketing Analysis

### 2015-12-16 2_marketing_analysis/marketing_analysis.Rmd
on hold

1. `revenue1` Aggregate each customer's total purchased amount for the current year.
2. `actual2` Merge the previous year's segment with this year's revenue, this is essentially examining how did our customers from last year performed this year. If a customer has not purchased anything for the current year then they will not show up in the revenue1 data ( resulting in NA values ) and we'll replace these values with 0.
3. Compute `revenue_average`: the average revenue that you would expect from each segment's customer in the next time period ( in our example, next year ). `revenue_total`: expected total revenue generated by each segment.

@@

# 1.
revenue1 <- data[ purchase_year == 2015, 
				  .( revenue = sum(purchase_amount) ), by = customer_id ]
# 2.
revenue2 <- merge( rfm2, revenue1, by = "customer_id", all.x = TRUE )
revenue2[ is.na(revenue), revenue := 0 ]

# 3. average revenue
revenue_average <- revenue2[ , .( avg_revenue = mean(revenue) ), by = segment ] %>%
				   arrange( desc(avg_revenue) )

# total revenue
revenue_total <- revenue2[ , .( avg_revenue = sum(revenue) ), by = segment ] %>%
				 arrange( desc(avg_revenue) )

list( revenue_average, revenue_total )

@@

From the printed result, we can infer interesting facts about our customer segment. For the `revenue_average` data.table, each "`r revenue_average$segment[1]`" customer is worth approximately `r round(revenue_average$avg_revenue[1])` to our company ( or you can say contribute that much do our company if the previous statement sounded a bit rude ... ). This is a lot higher than a "`r revenue_average$segment[ nrow(revenue_average) ]`" customer, which is at the bottom of the average revenue list. However, when we switched to the `revenue_total` data.table, it tells us that `r revenue_total$segment[1]` is the segment that generated the most revenue in total! If we looked back at our original `rfm2` segmentation ( scroll back up please ), we can also see that the customer size of this segment is around 20 percent and the second highest segment `r revenue_total$segment[1]` represents only about 3 percent of our entire customer. This is a good example where small segments in terms of number of customers that generates a huge share of revenues. And it's directly of telling us that customers should not be treated equally as there are just some that contributes more to the overall revenue.

>>>>

1. `revenue_per_customer` Aggregate each customer's total purchased amount for the current year.
2. `revenue_predicted` Merge the previous year's segment with this year's revenue, this is essentially examining how did our customers from last year performed this year. If a customer has not purchased anything for the current year then they will not show up in the revenue1 data ( resulting in NA values ) and we'll replace these values with 0.
3. `revenue_summary`: The average revenue that you would expect from each segment's customer in the next time period ( in our example, next year ) and the expected total revenue generated by each segment.

@@

# 1.
revenue_per_customer <- data[ purchase_year == 2015, 
				  			  .( revenue = sum(purchase_amount) ), by = customer_id ]
# 2.
revenue_predicted <- merge( rfm2, revenue_per_customer, by = "customer_id", all.x = TRUE )
revenue_predicted[ is.na(revenue), revenue := 0 ]

# 3. 
revenue_summary <- revenue_predicted[ , .( avg_revenue 	 = mean(revenue),
								  		   total_revenue = sum(revenue) ), by = segment ] %>%
				   arrange( desc(total_revenue), desc( avg_revenue) )
revenue_summary

@@

From the printed result, we can infer interesting facts about our customer segment. The average revenue column of the `revenue_summary` data.table tells us that each "`r revenue_summary$segment[2]`" customer is worth approximately `r round(revenue_summary$avg_revenue[2])` to our company ( or you can say contribute that much do our company if the previous statement sounded a bit rude ... ). This is a lot higher than a "`r revenue_summary$segment[ revenue_summary$segment == "inactive" ]`" customer. However, when we switched to the total revenue column, it tells us that `r revenue_summary$segment[1]` is the segment that generated the most revenue in total! If we looked back at our original `rfm2` segmentation ( scroll back up please ), we can also see that the customer size of this segment is around 20 percent and the second highest segment `r revenue_summary$segment[2]` represents only about 3 percent of our entire customer. This is a good example where small segments in terms of number of customers that generates a huge share of revenues. And it's directly of telling us that customers should not be treated equally as there are just some that contributes more to the overall revenue.
